The scientists participating in this coordinated project are part of the PETALO collaboration
whose purpose is to develop a new type of  high-sensitivity, nuclear magnetic resonance compatible, positron-electron tomography (PET) device, with enhanced Time Of Flight (TOF) sensitivity. PETALO is based in the Liquid Xenon Scintillating Cell (LXSC), as the basic detection unit. The project foresees several development stages:
\begin{enumerate}
\item Construction and operation of PETALO-0, a demonstrator of the LXSC technology. 
\item Construction and operation of PETALO-4, a prof of concept of PETALO based in 4 LXSC.
\item Construction and operation of PETALO-SAP, a small animal PET deploying 10-20 LXSC.
\item Construction and operation of PETALO-FULL, a PET of large acceptance and large sensitivity.
\end{enumerate}

Specifically, this project addresses the first two stages of the program. The collaboration intends to apply to H2020 HEALTH funds for the development of further stages of PETALO.

PETALO relies in the technology developed by the NEXT experiment. As a result, the  collaboration includes a number of physicists and engineers involved in NEXT. In addition, this project involves several experts in nuclear instrumentation, nuclear medicine, imaging, and ASIC design. Last but not least, the collaboration has a strong foundation in the medical community granted through te participation of the GIBI230 group. Indeed PETALO is currently a three-party venture including:

\begin{enumerate}
\item {\bf The Instituto de Física Corpuscular (IFIC)}, a join venture between University of Valencia (UV) and the Spanish Council for Research (CSIC). The group is co-led by J.J. G\'omez-Cadenas (JJGC) and J. Díaz Medina (JDM).  JJGC is the spokesperson of NEXT, as well as the proponent of the LXSC idea and the PETALO concept. JDM, a senior physicist with extensive experience in nuclear physics instrumentation, has been a leading contributor of NEXT and is currently the IP of the DET subproject as well as the coordinator of this proposal. 
\item {\bf The Instituto de Imagen Molecular (I3M)}, a join venture between University Polytechnic of Valencia (UPV), the CIEMAT and the Spanish Council for Research (CSIC). The group includes J.F. Toledo (JFT), Raul Esteve (RE), Vicente Herrero Bosch (VHB) and Rafael Gadea (RG). JFT and RE have designed and implemented the front-end and DAQ of the NEXT experiment. VHB and RG (both of them co-IPs of the ASIC subproject) are leading electronics engineers with ample experience in ASIC design for PET applications.  
\item {\bf The  Biomedical Imaging Research Group (GIBI230)} from La Fe Health Research Institute. This is the research group of the Clinical Area of Medical Imaging of La Fe Polytechnics and University Hospital. The group is lead by the prestigious radiologist Luís Martí Bonmatí (LMB), and includes a dynamic team of medical doctors, engineers and nuclear physicists.  
\end{enumerate}

%The IFIC group will be in charge of the design, construction, testing and validation of the  PETALO-0 and PETALO-4 demonstrators. The I3M group will be in charge of the front-end electronics, DAQ and slow control. The GIBI230 group
% will be in charge of quality control and safety requirements for the deployment of PETALO-10 in a clinical environment, will provide access to animal farm available at the hospital la Fe, and will develop algorithms for imaging processing. In addition to the well defined sharing of responsibilities, the different teams will need to work closely, first in the commissioning of the prototypes in a non-clinical environment, then in the operation of PETALO-10 as small animal PET, and finally in the validation of PETALO as fully NMR compatible apparatus.  
